\section{The Two Models}
\label{sec:models}

\subsection{OG-Core: an overlapping-generations general-equilibrium model}
\label{sec:og}

We take \OGCore{} \citep{debacker_evans_ogcore} as given and describe only what the
channels touch; readers fluent in the Auerbach--Kotlikoff tradition
\citep{auerbach_kotlikoff_1987} can skim. It is an overlapping-generations
general-equilibrium model with households indexed by $\Ngen$ ages and $\Jinc$
lifetime-income groups, $\Mind$ production industries, $\Igood$ consumption goods, and a
government that closes its budget each period.

\paragraph{Households.}
A household's demand for good $i$ is unit-elastic above a Stone--Geary subsistence floor
\citep{stone_1954},
\begin{equation}
  c_{i,j,s,t} \;=\; \alpha_i\Bigl(\tfrac{(1+\tauc_{i,t})\,p_{i,t}}{\tilde p_t}\Bigr)^{-1}
                    c_{j,s,t} \;+\; c_{\min,i},
  \label{eq:hhdemand}
\end{equation}
where $\tilde p_t$ is the composite price and $c_{j,s,t}$ total real consumption from the
life-cycle saving problem. This is the entry point for the energy channels: the
consumption-tax wedge $\tauc_{i_e}$ raises the effective price of the energy good, and the
$\Ngen\times\Jinc$ structure turns a single price change into a distribution of incidence.

\paragraph{Firms.}
Each industry produces with a CES function of private capital, public capital, and
labour,
\begin{equation}
  Y_{m,t} = Z_{m,t}\Bigl[\gammam^{\frac1\varepsilon}K_{m,t}^{\frac{\varepsilon-1}\varepsilon}
    + \gamma_{g,m}^{\frac1\varepsilon}K_{g,t}^{\frac{\varepsilon-1}\varepsilon}
    + (1-\gammam-\gamma_{g,m})^{\frac1\varepsilon}L_{m,t}^{\frac{\varepsilon-1}\varepsilon}\Bigr]
    ^{\frac\varepsilon{\varepsilon-1}},
  \label{eq:prod}
\end{equation}
which collapses to Cobb--Douglas, $Y_{m,t}=Z_{m,t}K_{m,t}^{\gammam}K_{g,t}^{\gamma_{g,m}}
L_{m,t}^{1-\gammam-\gamma_{g,m}}$, when $\varepsilon=1$ (the case in our calibration,
\Cref{sec:calibration}). The capital first-order condition defines a cost of capital
\begin{equation}
  \rho_m \;=\; \frac{r+\delta-\taub_m\delta^{\tau}_m-\tau^{\mathrm{inv}}_m\delta}{1-\taub_m},
  \label{eq:rho}
\end{equation}
so that (at $\varepsilon=1$) capital demand is $K_m=\gammam p_m Y_m/\rho_m$ --- the relation
the worked example of \Cref{sec:ch-capint} turns on. Note that the capital \emph{share}
$\gammam$ enters factor \emph{demand} but is absent from the cost of capital $\rho_m$;
the investment incentives ($\tau^{\mathrm{inv}}$, $\delta^{\tau}$, $\taub$) enter $\rho_m$
but not the production exponents. This separation is what makes \chan{capital\_intensity}
and \chan{energy\_capex} genuinely distinct instruments.

\paragraph{Government and solution.}
The government levies a consumption tax $\tauc$, a business tax $\taub$, and capital and
labour taxes; issues debt; pays transfers; and invests a share $\alphaI$ of output in
public capital $\Kg$. \OGCore{} is solved both in steady state (SS) and along a
transition path (TPI); the channels write parameters before a solve and read prices
($r$, $w$, $p_m$), quantities ($Y$, $C$, $K$, $L$, and sectoral $Y_m$, $K_m$), fiscal
accounts, and the full $\Ngen\times\Jinc$ distribution afterward.

\subsection{CLEWS / OSeMOSYS: a least-cost energy-systems optimizer}
\label{sec:clews}

\CLEWS{} \citep{howells_clews_2013} is built on the open-source \OSeMOSYS{} optimiser
\citep{howells_osemosys_2011}. For an economics audience the cleanest way to read it is as
a linear program that chooses capacity and dispatch to meet exogenous energy-service
demand at least discounted system cost:
\begin{equation}
  \min_{\{\text{NewCapacity},\,\text{Activity}\}}
    \sum_{t}\beta_t\bigl(\text{capital}+\text{fixed O\&M}+\text{variable O\&M}+\text{fuel}\bigr)_t
  \label{eq:lp}
\end{equation}
subject to engineering and policy constraints: a \emph{commodity-balance} constraint
requiring supply to meet demand for each fuel or carrier in every intra-year timeslice and
year; capacity-adequacy and capacity-factor limits; fuel-availability limits; and
emissions caps or penalties. Timeslices capture the intra-annual load shape (peak versus
off-peak) that a single annual figure would hide.

The price that makes the coupling work is the \emph{levelized cost of electricity}
(LCOE) --- the all-in average cost of a unit of delivered power (capital recovery,
operation and maintenance, and fuel), reconstructed from the least-cost solution's costs
and generation (\Cref{sec:signal}, \Cref{def:fixedpoint}). The coupling uses this average
cost rather than the \emph{shadow price} on the commodity-balance constraint --- the
program's short-run marginal cost of the carrier --- because that shadow price is
degenerate here: it binds in only scattered years, so it is not a usable long-run price
and is reserved for scarcity analyses. The shadow price on a binding emissions cap is,
likewise, an implied carbon price. These prices, not bare cost totals, are the
load-bearing signals.

Two features matter for the coupling. First, the program optimises against a \emph{fixed}
demand: quantity demanded does not respond to the carrier price within \OSeMOSYS{}
(\Cref{ass:inelastic}), so the price elasticity must be supplied by \OGCore{}. Second, the
LP is a single perfect-foresight optimisation over all years at once, with no household,
no government budget, and no distribution --- the complements \OGCore{} provides. Its
outputs are the technology and fuel mix, capital requirements, emissions, and (when the
solver is configured to expose them) the commodity and emissions marginal costs.

\subsection{The structural mismatch}
\label{sec:mismatch}

The two solution concepts do not compose into one optimisation (\Cref{ass:hardlink}):
\OGCore{} traces an overlapping-generations transition through time while \OSeMOSYS{}
plans all years simultaneously under perfect foresight, and \OGCore{} exposes no scalar
welfare into which the energy LP could be folded. A simultaneous (``hard'') link is
therefore not available, and the staged soft link of \Cref{sec:framework} --- baseline,
extract signals, apply wedges, optionally iterate --- is the appropriate object. The
asymmetry is also complementary: \OGCore{} supplies the behaviour, fiscal closure, and
heterogeneity \OSeMOSYS{} lacks, while \OSeMOSYS{} supplies the technology, dispatch, and
emissions detail \OGCore{} lacks.
