\section{The Channels}
\label{sec:channels}

The coupling is realised as eight channels (\Cref{tab:channel-map}): four carry
\CLEWS{} signals into \OGCore{} (\chan{energy\_price}, \chan{investment},
\chan{capital\_intensity}, \chan{health}), two are policy instruments applied to both
models (\chan{carbon}, \chan{energy\_capex}), and two read \OGCore{} outputs back to
\CLEWS{} (\chan{discount\_rate}, \chan{demand}). Each is the composition of an
extractor and a wedge (\Cref{sec:signals-wedges}); we give, for each, the signal it
reads, the \OGCore{} object it moves, the first-order effect, and its maturity. The
\chan{capital\_intensity}/\chan{energy\_capex} pair (\Cref{sec:ch-capint}) is treated
at length, because verifying it cleanly against the model's own equilibrium conditions
both corrects a natural mislabeling and illustrates the discipline of
\Cref{sec:discipline}.

\begin{table}[t]
\centering\footnotesize
\caption{The eight channels. Direction: \textsc{c$\to$o} \CLEWS$\to$\OGCore{};
\textsc{p} policy (both sides); \textsc{o$\to$c} \OGCore$\to$\CLEWS{}.}
\label{tab:channel-map}
\begin{tabularx}{\linewidth}{@{}l c L L L@{}}
\toprule
\textbf{Channel} & \textbf{Dir.} & \textbf{\CLEWS{} signal} & \textbf{\OGCore{} object} & \textbf{First-order effect} \\
\midrule
\chan{energy\_price} & c$\to$o & energy-balance dual / cost ratio & $\tauc$ on energy good & demand $\downarrow$; regressive incidence \\
\chan{carbon} & p & carbon price (\$/tCO$_2$) & $\tauc$ + emissions penalty & demand $\downarrow$; emissions $\downarrow$ \\
\chan{investment} & c$\to$o & public grid/T\&D capex & $\alphaI \to \Kg$ & public capital $\uparrow$; crowding-out, debt \\
\chan{capital\_intensity} & c$\to$o & power-fleet capital-cost share & $\gammam$ (energy exponent) & energy price $\downarrow$; energy $K\downarrow$; labour share $\downarrow$ \\
\chan{energy\_capex} & p & ITC rate (policy response) & cost of capital (\texttt{inv\_tax\_credit}) & capital reallocates into energy ($K\uparrow$) \\
\chan{health} & c$\to$o & PM\textsubscript{2.5} emissions ratio & $\rho(s,t)$, $e(t,s,j)$ & mortality $\approx0$; morbidity $\uparrow$ labour \\
\chan{discount\_rate} & o$\to$c & --- & reads $\rp$ $\to$ DiscountRate & shifts build mix (via loop) \\
\chan{demand} & o$\to$c & --- & reads $Y_m/C_i$ $\to$ demand & more capacity (via loop) \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Energy price}\label{sec:ch-energy}
The \chan{energy\_price} function applies the consumption-tax wedge of
\Cref{eq:routeA} on the energy good $i_e$; households then face
$(1+\tauc_{t,i_e})p_{i_e,t}$, so energy demand falls and the composite price rises. The
channel is now fed the Philippines' \emph{real} \CLEWS{} electricity price---the
``auto'' source: the cost-of-electricity index where a curated workbook exists,
otherwise the \OSeMOSYS{} commodity-balance dual on the raw run---rather than an
illustrative shock. That price is near-flat for the Philippine scenario, so the
standalone effect is small; a controlled $+20\%$ stress is retained only for the
transmission comparison of \Cref{sec:routes}. Incidence is the channel's distinctive
output: with energy a partial necessity ($\cmin>0$), a recycled price change (the
\chan{clean\_incidence} variant) is regressive---the lowest-income group bears more of
it. Maturity: rung~A (\Cref{sec:routes}), now on the real dual.

\subsection{Carbon price}\label{sec:ch-carbon}
A single carbon price is applied once on both sides (\Cref{sec:discipline}, one-price
principle): in \OGCore{} as an add-on to the energy-good wedge,
$\Delta\tauc_{i_e}=\text{(carbon price)}\times\text{deflator}\times\text{carbon
intensity}/p^{b}_{i_e}$, and in \CLEWS{} as an emissions-penalty path. Because \OGCore{}
has no energy in production, only \emph{household} energy carbon is priced on the macro
side; industrial carbon is priced only in \CLEWS{}. Revenue is recyclable through
transfers. Magnitudes are illustrative until the unit/deflator bridge and the carbon
intensity are calibrated (\Cref{sec:calibration}).

\subsection{Investment (public capital)}\label{sec:ch-investment}
Public grid and transmission capex enters as an increment to the public-investment
share $\alphaI$ (as a fraction of GDP, on a finite ramp), accumulating into the public
capital stock $\Kg$ through its law of motion; $\Kg$ is productive via the public-capital
share $\gamma_{g}$. This is the channel in which crowding-out legitimately lives: if the
spending is debt-financed it competes for the savings pool, raising $r$ and displacing
private investment. In the Philippine scenario the public grid-capex delta is near zero
(the transition is generation-side), so the channel is close to inert here; its mechanics
are validated and its magnitude scales with a non-zero public delta.

\subsection{Capital intensity vs.\ capital demand: a worked example in channel discipline}
\label{sec:ch-capint}

Two channels represent the capital side of a capex-heavy generation build-out, and
separating them cleanly is instructive. The temptation is to read ``a clean power system
is capital-intensive'' as ``it pulls capital in.'' \OGCore{}'s own equilibrium conditions
show these are two structurally different instruments---the natural lever for the first
reading need not deliver the second---and give the framework a way to \emph{attribute},
rather than assert, the capital response.

\paragraph{The factor-share lever (\chan{capital\_intensity}).}
This channel (\texttt{channels.capital\_intensity}) raises the energy industry's capital
exponent $\gammam$ by the \CLEWS{} reform/base ratio of the power fleet's capital-cost
share. Under the calibration's Cobb--Douglas technology ($\varepsilon=1$), capital's
revenue share \emph{is} $\gammam$, so the firm's capital demand is
\begin{equation}
  K_m \;=\; \frac{(1-\taub_{m})\,\gammam\, p_m\, Y_m}
                 {\,r+\delta-\taub_{m}\delta^{\tau}_{m}-\tau^{\mathrm{inv}}_{m}\delta\,},
  \label{eq:Kfoc}
\end{equation}
an exact rearrangement of the capital first-order condition. Because the channel scales
$\gammam$ and nothing else, the entire user-cost wedge and the $(1-\taub)$ factor cancel
in the reform/base ratio---the lever leaves them, and the numeraire-pinned return $r$,
unchanged---leaving the identity
\begin{equation}
  \hat K_E \;=\; \hat\gamma_E \,\cdot\, \hat p_E \,\cdot\, \hat Y_E .
  \label{eq:Khat}
\end{equation}
The identity is the tool for \emph{reading} the result. On the M=8 Philippine solve
(\Cref{tab:capital-pair}), raising the energy capital exponent by $12.2\%$ turns out to
\emph{shed} energy capital, by $22.4\%$: the higher exponent cuts the sector's unit cost,
so under zero profit the electricity price collapses $42.8\%$; demand is elastic enough
that energy output \emph{rises} $20.9\%$; but the price fall shrinks the sector's revenue
$p_m Y_m$ by more than the exponent and output together add back, so capital---its
$\gammam$ share of that revenue---falls. The identity
$\hat K_E=\hat\gamma_E\hat p_E\hat Y_E$ reproduces the $-22.4\%$ to within $0.03\%$. The
sign is thus not obvious a priori---raising the capital \emph{share} does not draw capital
in---and the framework attributes the response exactly. \chan{capital\_intensity} is a
factor-share and energy-price lever, not a capital-draw-in.

\paragraph{The capital-demand lever (\chan{energy\_capex}).}
The capital-draw-in force is a structurally different instrument
(\texttt{channels.energy\_capex}, a defined channel not exercised as a standalone run in
the present battery): an investment tax credit lowers the energy sector's \emph{cost of
capital}---it enters the user-cost denominator of \cref{eq:Kfoc} through
$\tau^{\mathrm{inv}}$, where $\gammam$ is \emph{absent}---shifting capital demand outward
at the prevailing $r$. That $\gammam$ moves factor \emph{demand} while the ITC moves the
\emph{cost of capital} is a structural fact of the firm block (\Cref{sec:og}), independent
of calibration: they are genuinely different levers, and the no-double-counting principle
(\Cref{sec:discipline}) forbids treating them as substitutes.

\begin{table}[t]
\centering\footnotesize
\caption{The \chan{capital\_intensity} channel decomposed via the firm identity
\cref{eq:Khat}, measured on the M=8 Philippine solve (energy industry $m_e=2$). Raising
the capital exponent collapses the electricity price and, despite higher output, sheds
capital; the identity reproduces the observed capital response to $0.03\%$. Source: the
solved steady states behind \texttt{results/golden.json}.}
\label{tab:capital-pair}
\begin{tabular}{@{}lrrrrr@{}}
\toprule
 & $\hat\gamma_E$ & $\hat p_E$ & $\hat Y_E$ & $\hat K_E$ (obs.) & identity $\hat\gamma_E\hat p_E\hat Y_E$ \\
\midrule
energy industry & $+12.2\%$ & $-42.8\%$ & $+20.9\%$ & $-22.4\%$ & $-22.4\%$ \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{The lesson.}
The two levers act on different objects---a production exponent versus the cost of
capital---so they are not interchangeable ``views of one capex,'' and the
no-double-counting principle
(\Cref{sec:discipline}) forbids treating them as substitutes or stacking them. More
broadly, this is the value of coupling to a structural general-equilibrium core: the
model's own first-order condition, \cref{eq:Kfoc}, is what exposes the mislabeling that a
partial-equilibrium intuition (``a higher capital share pulls capital in'') would
otherwise smuggle into the results.

\subsection{Health: emissions to demography and labour}\label{sec:ch-health}
The \chan{health} channel maps the reform/base PM\textsubscript{2.5} emissions ratio,
through external Global Burden of Disease age profiles, onto two demographic objects.
\emph{Mortality}: a shock to age-specific mortality $\rho(s,t)$, with the scale calibrated
to hit a signed excess-deaths target (a cleaner reform implies a negative target---lives
saved), after which the population is recomputed. Because PM\textsubscript{2.5} mortality
skews elderly, saved lives are mostly retirees, so the long-run output effect is near
zero. \emph{Morbidity}: the effective-labour profile $e(t,s,j)$ is scaled by a
working-age disability shape, so a cleaner reform raises labour productivity---the main
macro gain. The sign of the GDP effect therefore depends on horizon (a near-term morbidity
gain, a steady-state composition that adds retirees). The demographic inputs are
real: the Philippine ambient-PM\textsubscript{2.5} burden and its age profile come from
the Global Burden of Disease export ($43{,}951$ attributable deaths), scaled by a
calibrated per-country dose-response $M\approx0.082$ (an energy mass-share $\times$
concentration-response elasticity). The lives effect is
$\Delta\text{deaths}=\text{total}\times M\times\Delta\text{emissions}$, so the reform's
$-7.7\%$ emissions change saves about $279$ lives---the dose-response $M$ is what
separates this from the naive $43{,}951\times\Delta\text{emissions}\approx-3{,}400$. What
remains a modelling assumption---and keeps the channel reduced-form---is the
\emph{linearity} of that mapping and the size of the morbidity productivity elasticity,
not the burden or the dose-response. The mechanism itself---endogenous demography driven
by an emissions signal---is distinctively what an overlapping-generations core adds.

\subsection{Discount rate (\OGCore{} to \CLEWS{})}\label{sec:ch-discount}
After the reform solves, this channel reads \OGCore{}'s equilibrium market return $\rp$
(a multi-period mean) and writes it to \CLEWS{}'s \texttt{DiscountRate}, so that energy
planning uses the model-consistent cost of capital: a lower $\rp$ favours capital-heavy,
long-lived assets. The effect on the macro economy returns only once the soft link
iterates (\Cref{sec:architecture}); standalone, it is inert by construction.

\subsection{Demand (\OGCore{} to \CLEWS{})}\label{sec:ch-demand}
Symmetrically, this channel reads a reform/base activity ratio (industry output $Y_m$ or
consumption $C_i$, raised to an elasticity) and scales \CLEWS{}'s annual demand. In a
single pass the ratio is $\approx1$, so the channel is latent; it becomes a genuine driver
only inside the iterated loop---the macro-to-energy quantity link in the
\textsc{message-macro}/\textsc{times-macro} tradition
\citep{messner_schrattenholzer_2000,loulou_times_2008}.

\subsection{Policy levers}\label{sec:levers}
Channels couple the energy system; \emph{policy levers} are the generic, country-agnostic
primitives that vary a scenario, all using existing \OGCore{} parameters: an investment
incentive (the ITC behind \chan{energy\_capex}; sets \texttt{inv\_tax\_credit},
\texttt{delta\_tau}, $\taub$), a capital-share shift (the $\gammam$ behind
\chan{capital\_intensity}), revenue routing (to transfers $\alphaT$, public investment
$\alphaI$, government consumption, or deficit), and an industry registry derived from the
onboarded model rather than hard-coded. The capital pair of \Cref{sec:ch-capint} is the
clearest illustration: two levers ($\gammam$ and the ITC) instantiate two distinct
channels for one physical build-out, and the framework keeps them separate.
