\section{Calibration and Data}
\label{sec:calibration}

\paragraph{The economy.}
The macro side is the \texttt{ogphl} multi-sector calibration of \OGCore{}: $\Mind=8$
industries and $\Igood=5$ consumption goods, built from the country package's own
production and consumption structure (its \texttt{PROD\_DICT}/\texttt{CONS\_DICT} and
social accounting matrix). The link does not hard-code this structure: it is
\emph{discovered} per run in the \OGCore{} environment and exported to the link through a
\texttt{baseline\_meta.json} concordance, which records how many industries and goods the
country resolves and which of them is electricity---here industry $m_e=2$ and energy good
$i_e=1$. Where a country's aggregation cannot isolate electricity as its own industry and
good, the energy channels report a skip rather than mis-target (\Cref{sec:signals-wedges}).
Production is Cobb--Douglas ($\varepsilon=1$), with the public-capital share
$\gamma_{g}$ carved out of each industry's capital share so that labour's residual share
is well defined.

\paragraph{The energy price.}
The electricity price handed to the macro side is the country's \emph{real} \CLEWS{}
price---the ``auto'' source: a curated cost-of-electricity index where available,
otherwise the \OSeMOSYS{} commodity-balance marginal cost on the raw run---taken as a reform/base
ratio so the (uncalibrated) money units cancel. For the Philippine scenario pair this
ratio is near-flat. It is transmitted through the composite of \Cref{sec:routes}: an
inter-industry cost-push weighted by electricity's input-cost share $\phi_j$ across
industries (read from the SAM), with electricity's own self-use carried instead by a
recycled household wedge on the electricity value-share of the energy good. The direct
and indirect cost-push follows the standard input--output logic of \Cref{eq:routeB}; the
specific pass-through magnitudes are calibration-dependent and re-derived with the SAM
(the earlier M=4 figures are retired with that aggregation).

\paragraph{Health.}
The health channel uses \emph{real} epidemiological data: the ambient-PM\textsubscript{2.5}
attributable burden and its age profile from the IHME Global Burden of Disease export
(covering several countries; for the Philippines $43{,}951$ attributable deaths, with real
deaths-by-age and years-lived-with-disability-by-age profiles), scaled by a calibrated
dose-response $M\approx0.082$ (an energy mass-share $\times$ concentration-response
elasticity). The lives effect is
$\Delta\text{deaths}=\text{total}\times M\times\Delta\text{emissions}$, so the reform's
$-7.7\%$ emissions change saves about $279$ lives (the $\times M$ dose-response separates
this from the naive $43{,}951\times\Delta\text{emissions}\approx-3{,}400$). The remaining
modelling assumptions are the \emph{linearity} of that mapping and the morbidity
productivity elasticity, not the burden or the dose-response.

\paragraph{Units.}
The one uncalibrated bridge is the deflator that maps \CLEWS{} money to the \OGCore{} real
numéraire, currently set to unity. It affects the \emph{levels} of the carbon and
investment channels (and any revenue figure), though not the ratio-based energy price or
the demographic health inputs.

\caveat{Magnitudes for the carbon and investment channels are illustrative until the
unit/deflator bridge is calibrated; the \emph{mechanics} are validated (\Cref{sec:results})
and the \emph{sizes} scale with the bridge. The energy-price and health inputs are real
(a \CLEWS{} price ratio and the GBD burden).}
