% ==========================================================================
% OG-Core x CLEWS/OSeMOSYS — THE COUPLING MECHANISMS: A REFERENCE.
% One entry per channel: the intuition, then the technical form, then the
% variables. Companion to the deck (mechanisms.tex) and the paper (../paper);
% numbers are the committed M=8 Philippine golden record.
% Build: latexmk -pdf mechanisms-reference.tex
% ==========================================================================
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{xcolor}
\input{theme/ogclews-colors}
\usepackage[colorlinks=true,linkcolor=ogc,citecolor=ogc,urlcolor=clews]{hyperref}

% ---- notation (consistent with the deck and paper) ---------------------------
\newcommand{\OGCore}{\textsc{OG-Core}}
\newcommand{\CLEWS}{\textsc{CLEWS}}
\newcommand{\OSeMOSYS}{\textsc{OSeMOSYS}}
\newcommand{\tauc}{\tau^{c}}
\newcommand{\taub}{\tau^{b}}
\newcommand{\alphaI}{\alpha_{I}}
\newcommand{\alphaT}{\alpha_{T}}
\newcommand{\Kg}{K_{g}}
\newcommand{\gammam}{\gamma_{m}}
\newcommand{\gammag}{\gamma_{g}}
\newcommand{\rp}{r_{p}}

% ---- per-mechanism template --------------------------------------------------
\newcommand{\dir}[1]{\nolinebreak\hfill{\normalfont\small\color{mute}[#1]}}
\newcommand{\Intuition}{\par\smallskip\noindent{\color{ogc}\bfseries Intuition.}\ }
\newcommand{\Technical}{\par\smallskip\noindent{\color{clews}\bfseries Technical.}\ }
\newcommand{\Variables}{\par\smallskip\noindent{\color{sub}\bfseries Variables.}\ }

\setlist[itemize]{leftmargin=1.4em, itemsep=1pt, topsep=2pt}

\title{\vspace{-1.2cm}\bfseries OG-Core\,$\times$\,CLEWS --- The Coupling Mechanisms}
\author{}
\date{A reference: the intuition, then the technical form, for each channel.\\
\small Numbers are the committed M=8 Philippine golden record.}

\begin{document}
\maketitle
\vspace{-0.8cm}

% ==========================================================================
\section{The coupling in brief}

\OGCore{} and \CLEWS{} describe different parts of the same transition. \CLEWS{}/\OSeMOSYS{}
is a least-cost energy-system optimiser: it represents technologies, dispatch, investment,
and emissions in detail, but treats energy demand as an external input and has no
households, government budget, or distributional accounts. \OGCore{} is an
overlapping-generations general-equilibrium economy: it represents households (by age
$s$ and lifetime income $j$), firms ($M$ industries), and a government budget, but has no
priced energy input in firm production.

The models are therefore connected by a \emph{staged soft link}. A small set of solved
\CLEWS{} outcomes is translated into \OGCore{} parameters; selected \OGCore{} outcomes can
then be passed back to \CLEWS{} in the next iteration. The link is staged rather than
simultaneous because the models solve time differently: \OGCore{} moves through the
transition period by period, while \CLEWS{} optimises the full planning horizon at once.

Three objects organise every mechanism:
\begin{itemize}
  \item \textbf{Signal} --- an outcome read from a \emph{solved} \CLEWS{} scenario, such as
    an electricity price (its levelized cost), required grid investment, or emissions.
  \item \textbf{Wedge} --- the \OGCore{} parameter used to carry that signal: for example
    the consumption tax $\tauc$, industry productivity $Z_m$, public investment $\alphaI$,
    mortality $\rho(s,t)$, or effective labour $e(t,s,j)$.
  \item \textbf{Channel} --- the rule that maps one signal into one wedge, plus a
    diagnostic check for cases where the mapping is too large or poorly defined.
\end{itemize}

The main signal is the \textbf{energy price}: the levelized cost of electricity --- the
all-in average cost (capital, running costs, and fuel) of a delivered unit, reconstructed
from the solved \CLEWS{} system. In \OGCore{} this signal does two things \CLEWS{} cannot do on
its own: it lets quantities respond to price, and it shows which households and
industries bear the cost. Because \OGCore{} firms do not buy energy explicitly, the
electricity-price channel uses one composite transmission. It applies a cost-push to
industries that use electricity as an intermediate input, and a consumption wedge to
households that buy energy directly. The first part captures the contractionary,
wage-bearing effect; the second captures the distributional cost-of-living effect. The
input side is reduced-form: the fully structural version would add energy as a priced
production input.

Throughout, a hat denotes a reform/baseline ratio ($\hat x \equiv x^{r}/x^{b}$), and
$i_e$ / $m_e$ are the energy \emph{good} / \emph{industry} (Philippines: $m_e=2$).

% ==========================================================================
\section{The mechanisms}

The channels split by direction. Four carry \CLEWS{} signals into \OGCore{}, two are
policy levers applied consistently across the linked models, and two send \OGCore{}
outcomes back to \CLEWS{}.

\subsection{Energy price \dir{CLEWS $\to$ OG}}
\Intuition An electricity-price change enters the economy through production and
household consumption. Industries buy most electricity as an \emph{input} (about $73\%$
in the Philippine accounts), so a higher price raises production costs and affects
output, wages, and returns. Households buy electricity \emph{directly} (about $25\%$), so
the same price increase raises living costs. The proportional effect is larger for poorer
households because energy takes a larger share of their budgets. This channel carries
both uses together.
\Technical The reform/baseline electricity-price ratio $g$ is applied through both uses.
\emph{(i) Firm input --- cost-push:} each industry $j$'s productivity is cut by
electricity's share $\phi_j$ of its input costs (from the SAM),
$Z_j \mapsto Z_j/(1+\phi_j(g-1))$, so its output price rises by $\approx\phi_j(g-1)$ ---
the contractionary, wage-bearing side. \emph{(ii) Household consumption --- wedge:} a
consumption-tax wedge on the energy good, scaled to electricity's value-share $\sigma$ of
that good,
\[
  1+\tau^{c,r}_{i_e} \;=\; \bigl(1+\sigma(g-1)\bigr)\bigl(1+\tau^{c,b}_{i_e}\bigr)
\]
--- the regressive cost-of-living side. The additional revenue can be rebated to households
as transfers when the run uses revenue recycling. The electricity industry's own purchases of
electricity are removed from the cost-push to avoid double-counting through the household
wedge. The price $g$ is taken from \CLEWS{}'s automatic price source: a
cost-of-electricity index if available, otherwise the levelized cost of electricity
reconstructed from the run's costs and generation. In the Philippine run it rises about
$5\%$ on average (up to $16\%$ by 2030); the standalone channel is still small
($-0.006\%$ of steady-state output).
\Variables $g=\pi^{r}/\pi^{b}$, the reform/baseline electricity-price ratio; $\phi_j$,
electricity's share of industry $j$'s input costs; $\sigma$, electricity's value-share of
the household energy good $i_e$; $Z_j$, industry $j$'s productivity; $\tau^{c}_{i_e}$, the
consumption-tax wedge on the energy good ($r,b$ = reform, baseline).

\subsection{Carbon price \dir{policy --- both models}}
\Intuition The carbon price is a policy input applied once. In the energy model, it tilts
investment toward cleaner technologies. In the economy, it raises the price of household
energy like a tax. It is not also inferred from \CLEWS{}'s implied carbon cost, because
that would count the same policy twice.
\Technical A price $cp$ (US\$/tCO$_2$) becomes an add-on to the energy-good wedge in
\OGCore{}, and an emissions-penalty path in \CLEWS{}:
\[
  \Delta\tauc_{i_e} \;=\; \frac{cp \,\cdot\, \text{deflator}\,\cdot\,\text{carbon intensity}}{p^{b}_{i_e}}.
\]
Because \OGCore{} firms do not buy energy, the macro-side wedge covers only
\emph{household} energy carbon; industrial carbon is priced in \CLEWS{}. Revenue can be
recycled as transfers ($\alphaT$). Applied by itself, this channel changes steady-state
output by $-0.021\%$; that level should be read as illustrative because the conversion
from \CLEWS{} monetary units to the \OGCore{} numéraire is not yet calibrated.
\Variables $cp$, the carbon price; the deflator maps \CLEWS{} money to the \OGCore{}
numéraire (currently $1$, uncalibrated); carbon intensity, tCO$_2$ per unit of the energy
good; $\alphaT$, the transfer share used to recycle revenue.

\subsection{Public investment \dir{CLEWS $\to$ OG}}
\Intuition Grid expansion is public investment. If it is debt-financed, it competes for
savings, raises the interest rate, and can crowd out private investment. At the same
time, the resulting public capital is productive, so it can raise output. The net effect
depends on which force dominates.
\Technical The public grid-capex increment (as a share of GDP) is added to the
public-investment share $\alphaI$ on a finite ramp; it accumulates into public capital,
which is productive in the firm's technology:
\[
  K_{g,t+1} = (1-\delta)\,K_{g,t} + I_{g,t}, \qquad I_{g,t} = \alpha_{I,t}\,Y_t .
\]
This is where crowding-out enters the linked model. In the Philippine scenario the extra
grid spend is $\approx 0$ because the transition is mostly generation-side, so this
channel has essentially no effect here; the steady-state output change rounds to
$+0.000\%$. With non-zero grid spending, the same mechanics scale accordingly.
\Variables $\alphaI$, the public-investment share of output; $\Kg$, the public capital
stock; $I_g$, public investment; $\delta$, depreciation; $\gammag$, public capital's
share in production.

\subsection{Capital intensity \dir{CLEWS $\to$ OG}}
\Intuition A clean power fleet is capital-heavy: it has high up-front capex and low fuel
costs. That does not mean this channel necessarily pulls more capital into the energy
sector. Here the lever raises the energy sector's capital \emph{share} while holding
productivity fixed. In a competitive model, that lowers operating cost and pushes the
electricity price down. Because electricity demand responds only weakly, sector revenue
falls and the sector can shed capital. This channel is therefore a factor-income and
energy-price lever, not an investment-pull lever.
\Technical The reform/baseline ratio of the power fleet's capital-cost share scales the
energy industry's Cobb--Douglas capital share $\gammam$ (also its capital exponent;
Philippines: $+12.2\%$). Under Cobb--Douglas technology ($\varepsilon=1$), capital's
revenue share \emph{is} $\gammam$, so firm capital demand is
$K_m=\gammam\,p_m Y_m/\rho_m$. Taking reform/baseline ratios gives
\[
  \hat K_E \;=\; \hat\gamma_E \cdot \hat p_E \cdot \hat Y_E / \hat\rho_E .
\]
Here $\rho_m$ bundles the return, depreciation, business taxes, tax depreciation, and any
investment tax credit. This channel changes $\gammam$, not those user-cost terms; in the
Philippine solve $\hat\rho_E\approx 1$, so the result is read through the near-identity
\[
  \hat K_E \;=\; \hat\gamma_E \cdot \hat p_E \cdot \hat Y_E .
\]
Measured for the energy industry on an earlier M=8 steady-state solve of this lever:
$\hat\gamma_E=+12.2\%$, $\hat p_E=-42.8\%$, $\hat Y_E=+20.9\%$, so $\hat K_E=-22.4\%$; the
product $\hat\gamma_E\hat p_E\hat Y_E$ matches the result to $0.03\%$. The committed
golden records aggregates only (energy output $+4.4\%$, aggregate output $+0.001\%$ on
the re-blessed run); the sectoral price/capital decomposition is re-derived per solve.
\Variables $\gammam$, industry $m$'s capital exponent (its share of value added);
$\rho_m=(r+\delta-\taub_m\delta^{\tau}_m-\tau^{\mathrm{inv}}_m\delta)/(1-\taub_m)$, the
cost of capital; $p_m,Y_m$, the industry's price and output; a hat is a reform/baseline
ratio; $E$ marks the energy industry.

\subsection{Investment incentive \dir{policy}}
\Intuition To pull capital \emph{into} energy, lower the sector's cost of capital, for
example with an investment tax credit. That makes energy investment cheaper at the
prevailing interest rate, so capital reallocates toward the sector. This is distinct from
capital intensity: capital intensity changes the factor \emph{mix} in production, while
the credit changes the \emph{cost of capital}. They can move energy capital in opposite
directions.
\Technical An investment tax credit $\tau^{\mathrm{inv}}_m$ on the energy industry enters
the cost of capital directly, where the capital exponent is \emph{absent}:
\[
  \rho_m=\frac{r+\delta-\taub_m\delta^{\tau}_m-\tau^{\mathrm{inv}}_m\delta}{1-\taub_m}.
\]
A higher $\tau^{\mathrm{inv}}_m$ lowers $\rho_m$, so capital demand $K_m=\gammam p_m Y_m/\rho_m$
shifts out at the prevailing $r$. It is a defined lever, not part of the Philippine
reference run.
\Variables $\tau^{\mathrm{inv}}_m$, the investment tax credit rate; $\taub_m$, the
business-income tax; $\delta$, economic depreciation; $\delta^{\tau}_m$, tax depreciation;
$\rho_m$, the cost of capital.

\subsection{Health \dir{CLEWS $\to$ OG}}
\Intuition Cleaner air saves lives and, more important for output, makes working-age
people healthier and more productive. A $2.7\%$ cut in power-sector PM$_{2.5}$ does not
mean $2.7\%$ fewer pollution deaths. Power is only one source of pollution, and mortality
falls less than proportionally as air quality improves, so only about $8\%$ of the
emissions cut passes through to deaths. The avoided deaths are concentrated among older
people, so the long-run output effect is close to zero. The macro gain comes mainly from
working-age productivity during the transition.
\Technical The reform/baseline PM$_{2.5}$ emissions change $\Delta\text{em}$ scales the
country's Global Burden of Disease attributable deaths by a calibrated dose-response $M$:
\[
  \Delta\text{deaths} \;=\; D_{\mathrm{PM}} \times M \times \Delta\text{em}
  \;=\; 43{,}951 \times 0.082 \times (-0.0265) \;\approx\; -95 .
\]
\emph{Mortality} shocks the age-specific rate $\rho(s,t)$ to hit that signed target and
then recomputes the population; \emph{morbidity} scales the effective-labour profile
$e(t,s,j)$ by a working-age disability shape. Result: steady-state output changes by
$-0.0003\%$, but near-term output rises by $+0.19\%$. The $\times M$ term is what
separates $-95$ from the unadjusted $-1{,}165$.
\Variables $\Delta\text{em}$, the reform/baseline PM$_{2.5}$ emissions change;
$D_{\mathrm{PM}}$, GBD ambient-PM$_{2.5}$ attributable deaths ($43{,}951$, Philippines);
$M\approx0.082$, the dose-response (energy mass-share $\times$ concentration-response
elasticity); $\rho(s,t)$, mortality by age $s$ and time $t$; $e(t,s,j)$, effective labour
by time, age, and income group $j$.

\subsection{Discount rate \dir{OG $\to$ CLEWS}}
\Intuition The economy produces an equilibrium return on capital: its own cost of
capital. Passing that return to the energy planner lets \CLEWS{} discount future costs at
a rate implied by the macroeconomy rather than by an external assumption. A lower return
favours technologies with high up-front costs and long operating lives, such as
renewables.
\Technical After the reform solves, \OGCore{}'s equilibrium market return $\rp$ (a
multi-period mean) is written to \CLEWS{}'s planning discount rate. It is emitted
\emph{after} the solve and is one-way: it can change the energy build, but the resulting
prices feed back to \OGCore{} only in a later iteration. By itself it does not change the
current \OGCore{} solve.
\Variables $\rp$, the market portfolio return (\OGCore{}'s equilibrium cost of capital);
the \CLEWS{} discount rate it sets.

\subsection{Energy demand \dir{OG $\to$ CLEWS}}
\Intuition A larger or richer economy needs more energy. After \OGCore{} solves, its
activity level scales the demand path that \CLEWS{} must meet. In a single pass this
barely changes, so the channel mainly matters once the two models iterate.
\Technical The reform/baseline activity ratio (industry output $Y_m$ or consumption
$C_i$, raised to an elasticity) scales \CLEWS{}'s specified annual demand:
$\text{demand}^{r} = (\hat Y_m)^{\varepsilon_D}\,\text{demand}^{b}$. The signal is emitted
after the solve and is one-way. In one pass $\hat Y_m\approx 1$, so the demand path is
almost unchanged by construction.
\Variables $Y_m$, industry output; $C_i$, consumption of good $i$; $\varepsilon_D$, the
demand-scaling elasticity; the \CLEWS{} specified annual demand it scales.

\end{document}
