\section{Introduction}
\label{sec:intro}

How do the costs and benefits of a national resource-system plan---a country's
climate, land, energy and water strategy---propagate through the economy, and who
bears them? Countries develop these strategies with systems-planning models:
least-cost optimisers that choose capacity, dispatch, and resource allocation
subject to engineering and policy constraints, with the energy transition as the
leading current application. These models determine what the
plan is, but they cannot determine what the plan does to electricity prices, wages,
the cost of living, the public budget, or the distribution of welfare across
households, because they contain no households, no firms, no government, and no
prices that any agent responds to. The models that do contain these---general
equilibrium models of the macroeconomy---typically carry no energy technology: no
capacity constraints, no dispatch, no fuel mix, and no emissions accounting. The
economic questions raised by the energy transition therefore fall between two mature
modelling traditions, and they are increasingly consequential: carbon pricing is
spreading, national climate pledges must be costed, development finance is
conditioned on credible transition plans, and the distributional effects of energy
prices bear directly on whether reforms are politically sustainable.

In this paper we introduce a framework that connects the two traditions, and we show
what the connection makes it possible to answer. The framework links two open-source
models that countries already use. On the energy side is \CLEWS{}---Climate, Land,
Energy and Water Systems \citep{howells_clews_2013}---a least-cost planning framework
built on the \OSeMOSYS{} optimiser \citep{howells_osemosys_2011} and developed with
national teams so that each country owns its own model. On the economy side is
\OGCore{} \citep{debacker_evans_ogcore}, an overlapping-generations (OLG) general
equilibrium platform in the tradition of \citet{auerbach_kotlikoff_1987}, with
households differentiated by age and lifetime income, multiple industries, and a
government that closes its budget with explicit tax instruments. The two models are
connected by a channel-based soft link: a small set of economically meaningful
signals is read from the solved energy scenario---the electricity price, the required
grid investment, the emissions path---and each signal is carried into the economy by
exactly one model parameter, with the economy's equilibrium return and activity
passed back. Each channel is a named economic mechanism with stated assumptions, and
no signal enters twice. A companion paper \citep{lafleur_companion} develops the
framework formally and validates each mechanism; this paper motivates the link,
positions it within the literature on energy-macro integration, and illustrates its
use.

A substantial literature integrates energy-system and macroeconomic models, and we
review it in Section~\ref{sec:landscape}. Hard-linked models fold a stylised
one-agent growth economy into the energy optimisation
\citep{manne_wene_1992,messner_schrattenholzer_2000,manne_merge_1995,loulou_times_2008}.
Hybrid computable general equilibrium (CGE) models embed bottom-up technology in a
top-down economy \citep{bohringer_rutherford_2008,hourcade_hybrid_2006}, and
soft-linked national studies iterate an energy model against a CGE partner
\citep{krook_riekkola_2017,helgesen_tomasgard_2018}. Integrated assessment models
descending from \citet{nordhaus_dice_2008} address global abatement with aggregate
representations of both sides. These contributions establish that the integration
matters and how to organise it.

Existing approaches, however, share a common simplification: the macroeconomic side
has no age structure. The economy is a representative agent, or a set of households
differentiated by income but not by cohort, usually without forward-looking
life-cycle saving and without a fiscal sector that must close. This is precisely the
wrong simplification for the current generation of policy questions. The
distributional effects of energy prices differ across ages and generations
\citep{kotlikoff_2021}; the health co-benefits of decarbonisation operate through
demography, changing who is alive, at which ages, and with what productivity; and
fiscal closure is where carbon revenue, grid investment, transfers, and debt
interact. The OLG tradition carries exactly this structure, but it has not been
joined to a bottom-up energy-systems model. There is also a structural reason the
standard hard-link route cannot supply the connection: hard-linking requires the
economy to expose a scalar welfare objective the energy program can join, and an
OLG economy---an equilibrium among cohorts, not a planner's optimum---has none. To
our knowledge, the framework introduced here is the first to link a full
overlapping-generations economy to a bottom-up energy-water-land systems model.

We illustrate the framework with a Philippine application: the country's \CLEWS{}
case, a baseline against an announced energy-policy reform, coupled to a Philippine
multi-industry calibration of \OGCore{}. The link transmits the reform's real
electricity price---the levelized cost of electricity rises about $5\%$ on average,
peaking near $16\%$ around 2030---together with grid investment, a carbon price, and
the emissions-driven health channel. Three results illustrate what the coupled
framework can quantify. First, the macroeconomic effect of the reform changes sign
with the horizon: output rises by roughly $0.2\%$ over the first decade of the
transition but is $0.14\%$ below baseline in the long-run steady state. The near-term
gain operates through health---cleaner air raises working-age productivity---while
the long-run cost combines higher energy prices with a demographic composition
effect: the lives saved by cleaner air are concentrated among the elderly, so the
steady state has more retirees per worker. Second, the health effect is disciplined
by a calibrated dose-response: the reform's $2.7\%$ cut in power-sector particulate
emissions saves about $95$ lives per year, rather than the roughly $1{,}165$ implied
by scaling the attributable burden one-for-one. Third, incidence is regressive even
when the energy-price revenue is recycled to households as transfers: aggregate
consumption falls about $0.09\%$, with the burden concentrated on lower-income
households, for whom electricity is closer to a necessity. In each case the answer is
an output of the model rather than an assumption.

We position the paper within three strands of literature. First, we build on the
energy-macro integration literature
\citep{wene_1996,bohringer_rutherford_2008,hourcade_hybrid_2006}, adopting the
soft-link architecture but replacing the representative-agent macro partner with an
OLG economy, which the hard-link route cannot accommodate. Second, we complement the
OLG literature on climate and energy policy \citep{kotlikoff_2021}, which measures
generational incidence under aggregate representations of the energy system, by
supplying the bottom-up technology detail that national planning actually uses.
Third, we contribute to the quantification of health co-benefits
\citep{gbd_2019_risk,burnett_gemm_2018} by embedding them in general equilibrium as
demographic shocks---to survival rates and effective labour by age---rather than as
external valuations appended to an energy model's output.

Two design choices bear on how the results should be read, and we state them at the
outset. The link is soft and staged: the models remain separate programs exchanging
a small set of auditable files, because their solution concepts do not
compose---\OGCore{} traces a transition period by period while \OSeMOSYS{} optimises
all years at once. And the scope is deliberately limited: one full
\CLEWS{}$\to$\OGCore{} pass is implemented and validated against a committed
regression record; the reverse signals are emitted and ready, but the outer
fixed-point iteration is designed rather than closed, and the conversion between
\CLEWS{} monetary units and the \OGCore{} numéraire is an explicit bridge awaiting
calibration. The channel library is likewise currently instantiated for the energy
system---\CLEWS{}'s land and water signals enter through the same architecture and
are part of the extension roadmap (Section~\ref{sec:policy}). Magnitudes that depend
on the unit bridge are labelled illustrative wherever they appear.

The rest of the paper proceeds as follows. Section~\ref{sec:landscape} reviews how
energy-macro integration has been approached and identifies the gap the framework
fills. Section~\ref{sec:two-models} describes the two models and the rationale for
this pairing. Section~\ref{sec:linkages} presents the linkage framework: the
signal-wedge-channel structure, the electricity-price signal, and the eight
channels. Section~\ref{sec:illustration} reports the Philippine application.
Section~\ref{sec:policy} discusses implications for policy analysis and the
extension roadmap. Section~\ref{sec:conclusion} concludes.
