\section{Six Decades at the Seam: How Energy and Macro Models Have Been Joined}
\label{sec:landscape}

The energy-macro seam has been worked long enough to have a taxonomy. Four families
of solutions exist, and the differences between them come down to two questions:
\emph{how much economy} sits beside the energy technology, and \emph{how tightly} the
two are bound. This section reviews the families with an eye to a single test---can
the tool say who pays?---because that test is what motivates the link this paper
introduces.

\subsection{Hard links: an economy inside the optimiser}
\label{sec:hard-links}

The oldest and tightest approach folds a small macroeconomy directly into the energy
optimisation, so that one program solves both. MARKAL-MACRO \citep{manne_wene_1992}
attached a single-sector Ramsey growth model to the MARKAL energy system;
MESSAGE-MACRO \citep{messner_schrattenholzer_2000} did the same for MESSAGE,
iterating between the modules until they agree; MERGE \citep{manne_merge_1995} and
the TIMES family \citep{loulou_times_2008} carry the design forward. The gain is
real: energy demand responds to price \emph{inside} the solution, so the cost of a
constraint is measured against an economy that adapts.

The price of the tightness is the economy itself. For the macro side to sit inside
(or iterate cleanly against) an optimisation, it must be collapsed to a single
intertemporal utility function---one representative agent, one aggregate good, saving
determined by one Euler equation. There are no ages, no income classes, no separate
industries, no tax instruments, and no government budget in any meaningful sense.
The hard-linked family can say what a carbon constraint costs in aggregate
consumption; it cannot say who pays, because there is no one inside the model to pay
differently from anyone else. There is also a structural prerequisite worth naming,
since it explains why the approach cannot simply be repeated here: hard-linking
requires the economy to expose a scalar objective the energy program can join. An
overlapping-generations economy does not have one---it is an equilibrium among
cohorts, not an optimum of a planner---so the hard-link route is closed to exactly
the class of models that carries distribution.

\subsection{Hybrid CGE: technology inside the economy}
\label{sec:hybrid-cge}

The mirror-image approach embeds bottom-up technology detail into a top-down
computable general equilibrium model. The methodological landmark is
\citet{bohringer_rutherford_2008}, who showed how to formulate discrete energy
technologies and a full Arrow-Debreu economy as one mixed complementarity problem;
\citet{hourcade_hybrid_2006} frame the broader hybrid agenda. Applied descendants
run from global trade-and-energy CGEs to national policy models
\citep[e.g.][]{goulder_hafstead_2017}, and the tradition has produced serious
distributional work: \citet{rausch_2011} attach household micro-data to a CGE and
measure the incidence of carbon pricing across income classes.

Two limits persist. First, the economy is almost always \emph{recursive-dynamic}: it
rolls forward year by year with a fixed saving rule rather than solving forward-looking
life-cycle behaviour, so the intertemporal questions---who saves in anticipation of a
reform, how a transition redistributes across cohorts---are outside its language.
Second, even where households are heterogeneous by income, they are not
heterogeneous by \emph{age}: there are no cohorts, no retirement, no demography, and
therefore no way to express a mechanism as basic as ``cleaner air changes who is
alive and at what productive age.'' The hybrid CGE family can say who pays across the
income distribution in a given year; it cannot say who pays across generations, and
it cannot carry a demographic health channel at all.

\subsection{Soft links: two models, a negotiated agreement}
\label{sec:soft-links}

Between the poles sits the soft link: keep both models whole, pass results between
them, iterate to (approximate) consistency. \citet{wene_1996} formalised the
approach and its convergence logic; national implementations include the Swedish
TIMES-CGE pairing of \citet{krook_riekkola_2017}, and \citet{helgesen_tomasgard_2018}
study what full integration versus linking does to equilibria and convergence.
Soft links trade elegance for honesty: each model keeps its full structure and its
own solution concept, the exchange is inspectable, and the seam is explicit rather
than hidden inside a merged program.

The limitation of the soft-link literature is not the method but the partner: the
macro side has again been a representative-agent or income-class CGE, with the same
silences as Section~\ref{sec:hybrid-cge}. The method itself is exactly right for a
macro model that \emph{cannot} be hard-linked---which, as noted above, an OLG economy
structurally cannot. This paper is, in that sense, a soft link in the
\citet{wene_1996} tradition with a new class of partner on the economy side.

\subsection{Integrated assessment models: the seam at global scale}
\label{sec:iams}

Integrated assessment models answer a different question---the social cost of
carbon, optimal global abatement paths---and make different sacrifices to do so.
The DICE lineage \citep{nordhaus_dice_2008} reduces both sides of the seam: energy
technology to an aggregate abatement-cost function, the economy to a global Ramsey
planner. Process IAMs restore rich technology but keep the aggregate economy. The
family's central controversy is telling for our purposes: the debate between
\citet{stern_2007} and \citet{nordhaus_stern_2007} turned on a discount rate that
must be \emph{assumed}, precisely because a one-agent model has no market inside it
to reveal one. An economy with an equilibrium interest rate---as in the link
introduced here, where the energy planner's discount rate is read off the economy's
own cost of capital---dissolves a piece of that controversy by construction.

\subsection{The open cell in the taxonomy}
\label{sec:open-cell}

Arranging the families by their two coordinates---how much economy, how tight a
bind---reveals an open cell. Rich technology with a rich \emph{aggregate} economy
exists (hybrid CGE); rich technology with a thin optimising economy exists (hard
links, process IAMs); and OLG economies with rich fiscal and demographic structure
exist but with no energy technology attached---\citet{kotlikoff_2021} put carbon
policy into a full OLG world precisely to measure its generational incidence, but
with climate entering through an aggregate damage function, not through a power
system anyone plans. The cell that remains open is the one today's questions
occupy: \emph{bottom-up energy-water-land technology joined to an
overlapping-generations economy with fiscal closure}. Filling that cell requires a
soft link (the OLG side forbids hard-linking), a disciplined interface (so the
freedom of a soft link does not become arbitrariness), and a pair of models that
countries can actually own and run. The next two sections take these in turn.
