\section{The Two Models}
\label{sec:two-models}

\subsection{CLEWS}
\label{sec:clews-intro}

\CLEWS{} \citep{howells_clews_2013} is an integrated climate, land, energy, and
water planning framework built on \OSeMOSYS{} \citep{howells_osemosys_2011}, an
open-source linear program that chooses capacity additions and dispatch to meet
exogenous energy-service demands at least discounted system cost, subject to
engineering and policy constraints: capacity adequacy, fuel availability, emissions
caps or penalties, and the intra-annual load shape. Its outputs are the objects of
energy planning: the technology mix, the build schedule, fuel use, emissions, and
system costs.

Two properties make it the appropriate energy-side partner. First, it is
institutionally deployed: \CLEWS{} models are developed with national teams and
transferred to them, so the energy scenario a country couples to its economy is the
country's own plan rather than a stylised import. Second, its limitations are the
complementary ones: demand is a fixed input with no price response, and the model
contains no households, no government budget, and no distribution---system cost is a
total with no incidence attached to it.

\subsection{OG-Core}
\label{sec:og-intro}

\OGCore{} \citep{debacker_evans_ogcore} is an open-source overlapping-generations
general equilibrium platform in the tradition of \citet{auerbach_kotlikoff_1987}.
Households live through $S$ ages in $J$ lifetime-income groups, supplying labour,
saving, and consuming $I$ goods subject to a subsistence floor on necessities; $M$
industries employ labour and capital; and a government levies consumption, business,
and income taxes, issues debt, pays transfers, and invests in public capital, with a
budget that must close. The model solves both the long-run steady state and the full
transition path, so near-term and long-run effects are separately computable.
Countries calibrate the platform to their own accounts; the Philippine calibration
used below has eight industries and five consumption goods, with electricity
identified as its own industry and consumption good.

\OGCore{}'s limitations mirror those of \CLEWS{}: firms employ capital and labour
but no priced energy input, and the model carries no technology detail---no plants,
no dispatch, no emissions. What it uniquely contributes, relative to the
macroeconomic partners in Section~\ref{sec:landscape}, is the combination of
forward-looking life-cycle behaviour, age and income heterogeneity, demography that
policy can shift, and a fiscal sector with explicit instruments.

\subsection{The rationale for this pairing}
\label{sec:why-pair}

The pairing rests on three considerations. The first is structural complementarity:
each model's gap is the other's core competence, with little overlapping behaviour
to reconcile, so the double-counting problems that occupy much of the hybrid
literature largely do not arise. The second is institutional fit: both models are
open source, documented, and built for country ownership, so a coupled analysis can
be run, audited, and re-run by the country it describes---a requirement for policy
use rather than a convenience. The third is consistency of solution concepts: the
two models cannot be merged even in principle, since \OGCore{} traces a transition
period by period as an equilibrium among cohorts, \OSeMOSYS{} optimises all years
simultaneously for a planner, and the OLG economy exposes no scalar objective an
optimisation could join (Section~\ref{sec:hard-links}). A staged soft link---solve
the energy plan, carry a defined set of signals into the economy, solve the economy,
return its equilibrium rate and activity---is therefore the appropriate structure
rather than a second-best. What a soft link requires in exchange is discipline at
the interface, which the next section describes.
