\section{The Linkage Framework}
\label{sec:linkages}

The interface between the two models is organised around three objects. A
\textbf{signal} is a quantity read from a solved \CLEWS{} scenario: the electricity
price, the grid investment the build-out requires, the emissions path. A
\textbf{wedge} is the single \OGCore{} parameter that carries a signal into the
economy: a consumption-tax wedge, an industry productivity, the public-investment
share, a survival rate. A \textbf{channel} maps one signal to one wedge and attaches
a diagnostic guard that reports when the mapping is too large or ill-posed for the
reduced form to be reliable. Three rules give the interface its audit trail: every
signal enters through exactly one channel, so nothing is counted twice; every
channel is a named economic mechanism with stated assumptions, so nothing enters as
an opaque adjustment; and a channel whose data prerequisites a country cannot meet
reports a skip rather than substituting a fabricated input. The companion paper
\citep{lafleur_companion} states these as formal principles and validates each
mechanism; here we describe the channels and their economic content.
Table~\ref{tab:channels-glance} lists all eight.

\begin{table}[t]
\centering\small
\caption{The eight channels. C$\to$O carries a \CLEWS{} signal into \OGCore{};
O$\to$C returns an \OGCore{} outcome to \CLEWS{}; policy levers are applied once,
consistently, to both models.}
\label{tab:channels-glance}
\begin{tabularx}{\textwidth}{@{}l c L L@{}}
\toprule
\textbf{Channel} & \textbf{Dir.} & \textbf{Signal / lever} & \textbf{Carried by} \\
\midrule
Energy price & C$\to$O & electricity price (levelized cost) & industry cost-push $+$ household consumption wedge \\
Carbon price & policy & carbon price (\$/tCO$_2$) & energy-wedge add-on; emissions penalty in \CLEWS{} \\
Public investment & C$\to$O & grid build cost & public-investment share $\to$ public capital \\
Capital intensity & C$\to$O & power-fleet capital-cost share & energy industry's capital share \\
Investment incentive & policy & tax-credit rate & energy industry's cost of capital \\
Health & C$\to$O & PM$_{2.5}$ emissions change & survival rates $+$ worker productivity \\
Discount rate & O$\to$C & economy's equilibrium return & \CLEWS{} planning discount rate \\
Energy demand & O$\to$C & economy's activity change & \CLEWS{} specified annual demand \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{The price channels}
\label{sec:price-channels}

The principal signal is the electricity price, taken as the levelized cost of
electricity: the all-in average cost---capital recovery, operation and maintenance,
fuel---of a delivered unit, reconstructed from the solved system's costs and
generation, and passed as a reform/baseline ratio so that uncalibrated monetary
units cancel. The theoretically cleaner marginal cost, the shadow price on the
program's commodity-balance constraint, is degenerate in practice---it binds only in
scattered years---and is reserved for scarcity analyses. Transmitting the price to
the economy supplies the two elements the energy model lacks: quantities that
respond to price, and incidence.

Because \OGCore{} firms do not purchase energy explicitly, the price is transmitted
through the two uses of electricity in the country's own accounts. Industries
purchase most of it as an intermediate input (about $73\%$ of use in the Philippine
social accounting matrix), so each industry's productivity is reduced in proportion
to electricity's share of its input costs; this cost-push carries the output and
wage effects of the price change. Households purchase the remainder directly (about
$25\%$), so the energy good receives a consumption-tax wedge scaled by electricity's
value share $\sigma$ of that good:
\begin{equation}
  1+\tau^{c,r}_{i_e} \;=\; \bigl(1+\sigma(g-1)\bigr)\bigl(1+\tau^{c,b}_{i_e}\bigr),
  \label{eq:wedge}
\end{equation}
where $g$ is the price ratio and $i_e$ the energy good. This is the cost-of-living
side of the price change, and it is regressive because energy is a partial necessity
\citep{stone_1954}. The two components form one composite channel; the electricity
industry's own electricity use is netted out to prevent double counting. The carbon
price uses the same infrastructure as a policy lever applied once to both models: an
emissions penalty that shifts the \CLEWS{} build, and an add-on to the household
energy wedge on the macroeconomic side. It is deliberately not also inferred from
the energy model's implied carbon cost, which would price the same policy twice.

\subsection{The capital channels}
\label{sec:capital-channels}

Three channels carry the investment side of the transition, and the framework keeps
them separate because they act on different objects. Public investment adds the
grid's build cost to the public-investment share, which accumulates into productive
public capital; this channel is where crowding-out operates if the spending is
debt-financed. Capital intensity carries the higher capital share of a clean power
fleet into the energy industry's production technology, and its sign is not
automatic: a higher capital share lowers the sector's unit cost, the electricity
price falls, sector revenue falls, and the capital stock---which follows
revenue---can decline. The investment incentive, a tax credit, is the lever that
draws capital in, operating through the sector's cost of capital rather than its
factor shares. The three can move energy investment in opposite directions, and a
coupling that merged them into a single investment effect would lose distinctions
that are material for fiscal policy.

\subsection{The health channel}
\label{sec:health-channel}

The channel that requires age structure is health. Cleaner power reduces particulate
emissions, and the framework converts the reform's emissions change into lives and
labour using the country's Global Burden of Disease data \citep{gbd_2019_risk} and a
calibrated dose-response $M$ that reflects two facts: power generation is one source
of ambient pollution among several, and mortality responds less than proportionally
to concentration changes \citep{burnett_gemm_2018}. The mortality effect is
\begin{equation}
  \Delta\text{deaths} \;=\; D_{\mathrm{PM}} \times M \times \Delta\text{em},
  \label{eq:health}
\end{equation}
where $D_{\mathrm{PM}}$ is the attributable-deaths burden and $\Delta\text{em}$ the
emissions change. The results enter the economy as demographic shocks: avoided
deaths shift the age-specific survival rates, changing the population's age
composition, and morbidity gains scale the effective-labour profile of the
working-age population. Both wedges are age-specific. This is why the channel's
macroeconomic signature---a near-term productivity gain and a long-run increase in
retirees per worker---exists at all, and why it can be expressed only in a model
whose households have ages.

\subsection{The feedback channels}
\label{sec:feedback-channels}

Two channels run from the economy to the energy planner, after the economy solves.
The discount-rate channel writes \OGCore{}'s equilibrium market return---the first
decade's mean of the household portfolio return---into \CLEWS{}'s planning discount
rate, so that the energy planner discounts at the economy's own cost of capital
rather than at an assumed social rate. Given the sensitivity of least-cost plans to
this single parameter (Section~\ref{sec:iams}), harmonising it is substantive rather
than cosmetic. The energy-demand channel scales the demand path \CLEWS{} must meet
by the economy's solved activity change. In a single pass these channels stage the
next iteration; they are the interface of the loop closure discussed in
Section~\ref{sec:policy}.

\subsection{Limitations of the interface}
\label{sec:honesty}

Three simplifications are stated rather than implicit. The industry cost-push is
reduced-form: energy is not yet a priced production input, so the input side of the
price change is carried through productivity, calibrated by input shares. The
conversion between \CLEWS{} monetary units and the \OGCore{} numéraire is currently
set to unity, so the channels that depend on it (carbon and investment) have
validated mechanics but illustrative levels. And the coupling currently runs one
full pass; the return signals exist, but the fixed-point iteration between the
models is not yet closed. Each limitation is a defined interface with a designed
extension, and Section~\ref{sec:policy} returns to the roadmap.
