\section{A Philippine Illustration}
\label{sec:illustration}

We illustrate the framework with a Philippine application: the country's \CLEWS{}
case---a baseline against an announced energy-policy reform---coupled to the
Philippine multi-industry calibration of \OGCore{} ($M=8$ industries, $I=5$
consumption goods, with electricity identified as its own industry and good). All
inputs are the country's own data. The electricity price is the reform/baseline
levelized-cost ratio from the solved \CLEWS{} runs, about $1.05$ on average and
peaking near $1.16$ around 2030; the health inputs are the Philippine
ambient-PM$_{2.5}$ burden from the Global Burden of Disease ($43{,}951$ attributable
deaths, with deaths-by-age and disability-by-age profiles). The figures reported
below are the committed regression record of the coupled run. The purpose of the
exercise is to demonstrate the machinery on real inputs, not to evaluate the reform.

\subsection{The coupled result changes sign with the horizon}
\label{sec:headline}

\begin{table}[t]
\centering\small
\caption{The Philippine coupled run (percent change from baseline; steady state and
transition periods $t_0$, $t_{10}$).}
\label{tab:coupled-intro}
\begin{tabular}{@{}lrrr@{}}
\toprule
 & steady state & $t_0$ & $t_{10}$ \\
\midrule
output $Y$        & $-0.138$ & $+0.179$ & $+0.202$ \\
consumption $C$   & $-0.087$ & $+0.066$ & $+0.385$ \\
\bottomrule
\end{tabular}
\end{table}

The coupled reform---the real electricity price, grid investment, a
\$50/tCO\textsubscript{2} carbon price, and the health channel, applied
together---raises output by about $0.18\%$ on impact and $0.20\%$ a decade in, but
leaves it $0.14\%$ below baseline in the long-run steady state
(Table~\ref{tab:coupled-intro}, \Cref{fig:transition-intro}). The near-term gain
operates through the health channel: the reform's $2.7\%$ reduction in power-sector
particulate emissions raises working-age productivity, and this morbidity effect
dominates the early decades. The long-run reversal has two components: the
contractionary price channels accumulate, and the lives saved by cleaner air
(\cref{eq:health}: $43{,}951 \times 0.082 \times -0.0265 \approx -95$ per year) are
concentrated among the elderly, so the eventual steady state supports more retirees
per worker. The horizon structure is the substantive finding: an assessment based on
a single number---the steady state alone, or the impact effect alone---would reach
the opposite conclusion from an assessment based on the other, and none of the
approaches reviewed in Sections~\ref{sec:hard-links}--\ref{sec:iams} can represent
it.

\figurefig{coupled_transition}{The coupled transition path (percent change from
baseline): a positive near-term path driven by the working-age morbidity gain, and a
negative steady state in which the added retirees combine with the price
channels.}{fig:transition-intro}

\subsection{Channel-by-channel results}
\label{sec:channels-alone}

Run as standalone reforms, the channels behave as their mechanisms predict, and all
are small. The energy price alone moves steady-state output by $-0.006\%$: a real
$5\%$ price increase, transmitted faithfully, is not a large macroeconomic
shock---a discipline that is lost when stylised $+20\%$ shocks stand in for data.
Carbon is the largest single contraction at $-0.021\%$. Capital intensity barely
moves aggregate output while reshaping the energy sector. Health is $-0.0003\%$ at
the steady state but $+0.19\%$ near-term. The sum of the standalone effects
($\approx-0.02\%$) is an order of magnitude smaller than the coupled steady state
($-0.138\%$): the channels interact in general equilibrium, so the channel-by-channel
table is a diagnostic decomposition rather than an additive accounting---a caution
that applies equally to the common practice of costing policy packages one component
at a time.

\subsection{Incidence}
\label{sec:who-pays}

Incidence is the output the OLG structure exists to provide. Under the recycled
electricity-price experiment---the price change applied to households with all
revenue returned as transfers---aggregate consumption still falls ($-0.092\%$ at the
steady state), and the burden is concentrated on lower-income households, for whom
electricity lies closer to the subsistence floor of the demand system. Revenue
recycling softens but does not eliminate the regressivity. The result is a
quantitative distributional answer, by age and income group, produced by the same
framework that carries the energy plan.

\caveat{The energy-price and health inputs are real (a \CLEWS{} price ratio and the
GBD burden); the carbon and investment magnitudes depend on the uncalibrated
money-to-numéraire bridge and are illustrative. Mechanics are validated throughout;
levels are labelled.}
