\section{Discussion and Policy Implications}
\label{sec:policy}

\subsection{Questions the linked framework can answer}
\label{sec:new-questions}

The contribution of the link is a set of questions that move from outside the model
to outputs of the model. For an energy-transition package expressed as a \CLEWS{}
scenario, the coupled framework can now quantify: the incidence of the implied
electricity-price path by age and lifetime income, with and without revenue
recycling; the impact, medium-run, and steady-state effects, which can differ in
sign because the economy solves a full transition; the health co-benefits in lives,
age structure, and effective labour, from the country's own burden data; the fiscal
accounting, with carbon revenue, grid investment, transfers, and debt inside one
consistent budget; and the discount rate the plan itself should use, read from the
economy's equilibrium cost of capital rather than assumed
(Section~\ref{sec:feedback-channels}). Each answer is attributable to a named
channel, which is what makes the framework usable in policy argument: a contested
number can be traced to its mechanism, its signal, and its stated assumptions.

\subsection{Portability and country ownership}
\label{sec:ownership}

The framework is designed to be portable across countries. Both parent models are
open source. The link reads a country's existing \CLEWS{} case as produced by its
national team, and discovers the country's \OGCore{} calibration---how many
industries and goods it resolves, and which is electricity---at run time rather than
hard-coding any country's structure. Channels whose data prerequisites a country
cannot meet report a skip rather than fabricating an input. Applications require
four core country inputs: a solved \CLEWS{} scenario pair (baseline and reform), a
country calibration of \OGCore{} that identifies the electricity industry and good,
the social accounting matrix shares that allocate electricity use between industries
and households, and the country's burden-of-disease export where the health channel
is used. Given these inputs, the same structural mapping generates country-specific
transition paths for output, consumption, incidence, and the other welfare-relevant
aggregates. The intended user is the analyst in a ministry or country office who
already runs one of the two models and needs the other half of the answer, on
infrastructure the country controls and can audit.

\subsection{Limitations and extension roadmap}
\label{sec:scope}

Three limitations define the current scope, each with a designed extension. First,
the coupling runs one validated \CLEWS{}$\to$\OGCore{} pass; the return signals (the
equilibrium rate and activity) are emitted and ready, and closing the loop---
iterating until the electricity price the economy faces and the demand the planner
meets agree---is the next step. Second, the conversion between \CLEWS{} monetary
units and the \OGCore{} numéraire is not yet calibrated, so the carbon and
investment magnitudes are illustrative until the bridge is pinned to the country's
accounts. Third, energy enters firm costs in reduced form; the structural extension
prices energy as a production input within \OGCore{} itself. Fourth, the channel
library currently reads the energy side of a \CLEWS{} case; the land and water
sides carry economically analogous signals---food and crop prices, irrigation
investment, water scarcity---that enter through the same signal-wedge-channel
architecture, and extending the library to them is a natural next application. None
of these limitations is implicit in the output: illustrative levels are labelled
where they appear, and validated mechanics are distinguished from calibrated
magnitudes throughout.
